D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Add for shadowing of the newish Section 1.3
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Remove "references" question from section 1.1
On further thought, it does not seem like we really need a reference
for "syntactic dependency".  Of course, if there proves to be a nice
convenient reference, why not?

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

We begin with a brief overview of the OOTA problem followed by an equally
brief summary of prior OOTA work.

@@

A \emph{syntactic} dependency, by contrast, exists whenever the value
of the load appears in the source code as part of the computation
leading up to the store, whether it affects the store or not.
\emph{@@@ Reference?}
Although we will not give a precise definition of syntactic dependency
here, doing so presents no fundamental difficulties.
In fact, the C++ standard covers much of the same ground in its definition
of ``carries a dependency'' in 6.9.2.2p7 (\co{[Data races]}).
Of course, all semantic dependencies are also syntactic.
Note, however, that only semantic dependencies contribute to OOTA.

>>>>

We begin with a brief overview of the OOTA problem followed by an equally
brief summary of prior OOTA work and of our approach.

@@

A \emph{syntactic} dependency, by contrast, exists whenever the value
of the load appears in the source code as part of the computation
leading up to the store, whether it affects the store or not.
Although we will not give a precise definition of syntactic dependency
here, doing so presents no fundamental difficulties.
In fact, the C++ standard covers much of the same ground in its definition
of ``carries a dependency'' in 6.9.2.2p7 (\co{[Data races]}).
Of course, all semantic dependencies are also syntactic.
Note, however, that only semantic dependencies contribute to OOTA.
